Identifying regime transitions for water governance at the Yellow River Basin, China

### 2023-10-10 paper/out/manuscript_v-8.3.1.tex
docs(paper): :memo: v-8.3.1
submission version to WRR - RR

	\subsubsection{Indicator of stress (IS)}
	We used the scarcity-flexibility-variability (SFV) water stress index proposed by \citeA{qin2019} to evaluate water stress.
	This indicator integrates the share of runoff being consumed, the share of consumption in these inflexible categories and the historical variability of runoff weighted by storage capacity~\cite{qin2019}, where impacts from both management measures and climate changes are included.
The SFV-index, which has many applications, is the most comprehensive index of water stress we know.

@@

We used $\alpha = 0.001$ as the threshold level of the p-value, meaning that the probability of a statistically significant change-point judgment being valid was more than $99.9\%$. We divided the series into two at that point and analyzed each series separately until all significant change points were detected. Though two break points in the main text with $\alpha = 0.001$, the threshold from $0.0005$ to $0.05$ does not affect our results, and the breakpoints we identified are robust (see Figure~S6).

@@

Two significant breakpoints divide the changes in the IWGI into three periods, with different contributions from three aspects (Figure~\ref{fig:IWGI}A).
In the first period (P1, $1965 \sim 1978$), the IWGI decreased rapidly.
While the indicator of purpose and allocation contributed more to the IWGI ($49.45\%$ and $34.95\%$ on average, respectively), the remarkable downward trend correlates significantly ($p<0.01$) to the decreasing allocation and stress indicators (Figure~\ref{fig:IWGI}B).
In the second period (P2, $1979 \sim 2001$), the increasing stress indicator significantly ($p<0.01$) contributed to the upward IWGI, while the allocation and purpose indicators played negative roles in changing the IWGI.\
During the third period (P3, $1995 \sim 2013$), while the stress indicator kept its most prominent share in contributions ($57.11\%$ on average), the increased allocation indicator and decreased purpose indicator changed the regime.
Taken together, the overall features of the three aspects in different periods are relative to a directional change in the combination of three aspects (Figure~\ref{fig:IWGI}C).

@@

      \footnotesize
      $^*$ Social atmosphere refers to the sociocultural context in which people live or in which something happens, including the culture that the individual was educated or lives.
  \end{table}
The start of the governance transforming regime (P2: $1979 \sim 2001$) coincided with rising competition for water use after the ``reform and opening-up'' (Figure~\ref{fig:Causes}~C).
The results from the YRB mirror those of the theoretical analysis: continuous increases in water demand when the basin's total supply is stable can follow substantial changes in governance regime and a rapid enhancement in overall social adaptive capacity~\cite{loch2020}.
As a pioneer in shifting governing institutions, the YRB triggered institutional changes during this regime. These include, for example, slowing the growth of irrigated acreage and leading water-saving infrastructure (Figure~\ref{fig:Causes}); creation of China's first water quota scheme, and the creation of a preliminary cross-boundary water transfer plan~\cite{wang2019e,long2020,nickum2021}.
Consequently, although water stress remained and increased (due to reducing streamflow and flexibility), the last depletion of the Yellow River in 1999 led to a climax in this transformation in water governance~\cite{wang2019e}.

>>>>

	\subsubsection{Indicator of stress (IS)}
	We used the scarcity-flexibility-variability (SFV) water stress index proposed by \citeA{qin2019} to evaluate water stress.
	This indicator integrates the share of runoff being consumed, the share of consumption in these inflexible categories and the historical variability of runoff weighted by storage capacity~\cite{qin2019}, where impacts from both management measures and climate changes are included.
The SFV-index, which has many applications, is the most comprehensive index of water stress we know~\cite{qin2019}.

@@

We used $\alpha = 0.001$ as the threshold level of the p-value, meaning that the probability of a statistically significant change-point judgment being valid was more than $99.9\%$. We divided the series into two at that point and analyzed each series separately until all significant change points were detected. Though two break points in the main text with $\alpha = 0.001$, the threshold from $0.0005$ to $0.05$ does not affect our results, and the change points we identified are robust (see Figure~S6).

@@

Two significant change points divide the changes in the IWGI into three periods, with different contributions from three aspects (Figure~\ref{fig:IWGI}A).
In the first period (P1, $1965 \sim 1978$), the IWGI decreased rapidly.
While the indicator of purpose and allocation contributed more to the IWGI ($49.45\%$ and $34.95\%$ on average, respectively), the remarkable downward trend correlates significantly ($p<0.01$) to the decreasing allocation and stress indicators (Figure~\ref{fig:IWGI}B).
In the second period (P2, $1979 \sim 2001$), the increasing stress indicator significantly ($p<0.01$) contributed to the upward IWGI, while the allocation and purpose indicators played negative roles in changing the IWGI.\
During the third period (P3, $1995 \sim 2013$), while the stress indicator kept its most prominent share in contributions ($57.11\%$ on average), the increased allocation indicator and decreased purpose indicator changed the regime.
Taken together, the overall features of the three aspects in different periods are relative to a directional change in the combination of three aspects (Figure~\ref{fig:IWGI}C).

@@

      \footnotesize
      $^*$ Here, social atmosphere refers to the sociocultural context in which people live or in which something happens, including the culture that the individual was educated or lives.
  \end{table}
The start of the governance transforming regime (P2: $1979 \sim 2001$) coincided with rising competition for water use after the ``reform and opening-up'' (Figure~\ref{fig:Causes}~C).
The results from the YRB mirror those of the theoretical analysis: continuous increases in water demand when the basin's total supply is stable can follow substantial changes in governance regime and a rapid enhancement in overall social adaptive capacity~\cite{loch2020}.
As a pioneer in shifting governing institutions, the YRB triggered institutional changes during this regime. These include, for example, slowing the growth of irrigated acreage and leading water-saving infrastructure (Figure~\ref{fig:Causes}); creation of China's first water quota scheme, and the creation of a preliminary cross-boundary water transfer plan~\cite{wang2019e,long2020,nickum2021}.
Consequently, although water stress remained and increased (due to reducing streamflow and flexibility), the last depletion of the Yellow River in 1999 led to a climax in this transformation in water governance~\cite{wang2019e}.
